---
title: "Patstat to Postgre SQL Database"
output: html_notebook
---

# Setup

```{r}
# Not sure if necessary... was an issue with a version conflict... try new version in the future again...
# devtools::install_version("RPostgres", version = "1.2.1", repos = "http://cran.us.r-project.org")

### general options
Sys.setenv(LANG = "en")
options("scipen" = 100, "digits" = 4) # override R's tendency to use scientific notation

### Clean workspace
rm(list=ls())
graphics.off()

### setWD (maybe needs installation of rstudioapi package)
# require(rstudioapi); setwd(dirname(rstudioapi::getActiveDocumentContext()$path)); getwd()

### Load packages (maybe need to be installed first)
# Standard
library(tidyverse) # General DS toolkit
library(magrittr) # For advanced piping

# Databases
library(DBI) # GEneral R database interface
library(RPostgres) # PostgreSQL interface driver 
library(dbplyr) # for dplyr with databases
```

```{r}
# Outsourced in this script
source("R/functions.R")
```

# Preamble

## Define variables

First, we set up some variables, so the script runs on its own. 

* The first thing we have to do is to enter the information for connecting with the Postgre SQL database we want to populate with the PATSTAT data

```{r}
# Database access
var_dbname = "INSERT_YOUR_DB"
var_host = "INSERT_YOUR_HOST_ID"
var_port = 5432 # OR other
var_user = "INSERT_OUR_USER_NAME"
var_password = "INSERT_YOUR_PASSWORD"
```

* Next, we need to define the path (relative to our current working directory), where the downloaded PATSTAT files can be found.
* This files all have to be in the same folder.
* Therefore, unzip the `zip` files downloaded from PATSTAT twice until the results are `.csv` files (eg. `tls201_part01.csv`), and copy them all in the same folder.
* Attention: The `readr` package can also diectly read `zip` files, but it will truncate files >4gb (as all unzip options in R), therefore we have to manually do this.

```{r}
# PATSTAT folder
var_folder = "YORUDRIVE/YOURFOLDER"
```

... or load a scipt where you define the variables

```{r}
# LOad script with variables
source("../variables.R")
```



## Connect to database

We now establish a connection to the database.

```{r}
# set up connection to existing PostgreSQL database, just plug in own details
con <- dbConnect(drv = RPostgres::Postgres(), 
                 dbname = var_dbname,
                 host = var_host, 
                 port = var_port,
                 user = var_user, 
                 password = var_password,
                 sslmode = 'require'
                 )
```

```{r}
# Inspect DB:
con %>% dbListTables() %>% sort()
```


## Load adittional data: 

```{r}
# Overview of PATSTAT tables
table_names <- read_csv("data/PATSTAT_table_description.csv")
```

```{r}
file_list <- tibble(tbl_id = NA,
                    tbl_part = list.files(path = var_folder, pattern = "tls.*csv"),
                    tbl_path = paste(var_folder, tbl_part, sep = '/')) %>%
  mutate(tbl_part = gsub("\\.csv", "", .$tbl_part),
         tbl_id = gsub("\\_.*", "", .$tbl_part) ) %>%
  left_join(table_names, by = c('tbl_id' = 'table_id') ) %>% 
  mutate(tbl_name = paste(tbl_id, name, sep = '_'))
```


# Define the tables in Postgres


```{r}
# # To delete all tables
# rem <- dbListTables(con); rem <- rem[rem != 'users']; for(i in 1:length(rem )){dbRemoveTable(con, rem[i])}; rm(rem)

# # To delete specific tables
# rem <- dbListTables(con); rem <- rem[rem %in% c('users')]; for(i in 1:length(rem )){dbRemoveTable(con, rem[i])}; rm(rem)
```

The following outsourced

```{r}
source("R/script_create_tables.R")
```

```{r}
con %>% dbListTables() %>% sort()
```



# Populate the Potgres with PATSTAT data

##

```{r}
# Select or disselect certain rows
include_number <- 1:nrow(file_list)
include_name <- c('tls203') # Indicate by name the tables to include, if you want to exclude some by name
exclude_name <- c() # Indicate by name the tables to exclude, if you want to exclude some by name
```


```{r}
# subset the table
tbl_select <- file_list[include_number, ] %>% filter((tbl_id %in% include_name) & !(tbl_id %in% exclude_name))
rm(include_name, exclude_name)
```


##


```{r}
for(i in 1:nrow(tbl_select) ) {
  patstat_import_postgre(con = con,
                         tbl_path = tbl_select[i,] %>% pull(tbl_path),
                         tbl_name = tbl_select[i,] %>% pull(tbl_name),
                         append = TRUE,
                         overwrite = FALSE
  ) }
```



```{r}
tbl(con, 'tls203_appln_abstr') %>% head(100)
```



```{r}





# This loop imports all tables to the PostgreSQL database. You can instead also run the function sepperate for the tables
for(i in 1:nrow(table_select) ) {
  Patstat_to_PostgreSQL(con = con,
                        tbl = table_select[i,],
                        append = TRUE,
                        overwrite = FALSE
                        )
}
```











```{r}
f <- function(gear_val) {
  function(x, pos) {
    dplyr::filter(x, .data[["gear"]] == gear_val)
  }
}

readr::read_csv_chunked(
  readr::readr_example("mtcars.csv"),
  readr::DataFrameCallback$new(f(gear_val = 3)),
  chunk_size = 5
)
```








  




### Count rows

# TODO

##############################################################################
# Indexing
##############################################################################

# Outsourced in this script: You however might want to run it one by one
# Warning: This takes some hours...
source("000_create_index.R")

##############################################################################
# Create Foreign Key
##############################################################################

# Outsourced in this script: You however might want to run it one by one
source("000_create_foreign_key.R")

##############################################################################
# Clustering
##############################################################################

# Outsourced in this script: You however might want to run it one by one
# source("000_clustering.R")
# Note: Not done yet...


##############################################################################
# Disconnect
##############################################################################

dbDisconnect(con)
dbUnloadDriver(drv)




